Classless Java

### 2016-03-23 OOPSLA16/sections/CaseStudy.tex
revised text related to case studies

\section{Case Studies}
In this section we conduct \numOfCaseStudies case studies which reveal various
advantages of using the \mixin annotation. The first case study provides a
simple way to solve the Expression Problem while supporting multiple,
independent extensions in Java.  The second case study shows how to model an
embedded DSL for SQL languages with fluent interfaces. Finally, the third
case study models a simple game, and compares our implementation with an
existing one, showing that the amount of code is reduced significantly using \mixin.

@@

\begin{figure*}
\centering
\saveSpaceFig
\begin{tabular}{l|l}
\lstinputlisting[linerange=34-44]{../UseMixinLombok/src/casestudy/ep/TestExpression.java}% APPLY:linerange=EXPRESSION_INIT
&
\lstinputlisting[linerange=55-65]{../UseMixinLombok/src/casestudy/ep/TestExpression.java}% APPLY:linerange=EXPRESSION_PRINT
\end{tabular}
\caption{The Expression Problem (left: initial system, right: code for adding
  print operation).}\label{fig:ep}
\end{figure*}% \bruno{Yanlin: code is overflowing the margins. Note that
  % there are 2 spare lines that can be used on the right!}

@@

\lstinputlisting[linerange=48-51]{../UseMixinLombok/src/casestudy/ep/TestExpression.java}% APPLY:linerange=EXPRESSION_SUB

@@

\lstinputlisting[linerange=89-91]{../UseMixinLombok/src/casestudy/ep/TestExpression.java}% APPLY:linerange=INDEPENDENT_EXTENSIBILITY

>>>>

\section{Case Studies}
In this section we conduct \numOfCaseStudies case studies which reveal various
advantages of using the \mixin annotation. The first case study provides a
simple way to solve the Expression Problem while supporting multiple,
independent extensions in Java.  The second case study shows how to model an
embedded DSL for SQL languages with fluent interfaces. The third
case study models a simple game, and compares our implementation with an
existing one, showing that the amount of code is reduced significantly using \mixin.
Finally, the fourth one refactors an interpreter, showing that our approach  
benefits modularity and scales to larger and real code base.

@@

\begin{figure*}
\centering
\saveSpaceFig
\begin{tabular}{l|l}
\lstinputlisting[linerange=33-43]{../UseMixinLombok/src/casestudy/ep/TestExpression.java}% APPLY:linerange=EXPRESSION_INIT
&
\lstinputlisting[linerange=54-64]{../UseMixinLombok/src/casestudy/ep/TestExpression.java}% APPLY:linerange=EXPRESSION_PRINT
\end{tabular}
\caption{The Expression Problem (left: initial system, right: code for adding
  print operation).}\label{fig:ep}
\end{figure*}% \bruno{Yanlin: code is overflowing the margins. Note that
  % there are 2 spare lines that can be used on the right!}

@@

\lstinputlisting[linerange=47-50]{../UseMixinLombok/src/casestudy/ep/TestExpression.java}% APPLY:linerange=EXPRESSION_SUB

@@

\lstinputlisting[linerange=88-]{../UseMixinLombok/src/casestudy/ep/TestExpression.java}% APPLY:linerange=INDEPENDENT_EXTENSIBILITY

### 2016-03-23 OOPSLA16/sections/Introduction.tex
revised text related to case studies

To evaluate the usefulness of object interfaces, we illustrate
\numOfCaseStudies \bruno{needs updates}\yanlin{updated} 
applications. The first application is a simple 
solution to the Expression Problem~\cite{wadler98expression}, supporting independent 
extensibility~\cite{zenger05independentlyextensible}, and without boilerplate code. The second
application shows how embedded DSLs using fluent interfaces~\cite{fowler2005fluentinterface} 
can be easily defined using object interfaces. The third
application is a case study for a simple Maze game implemented with 
multiple inheritance. For this application we show that there is a
significant reduction in the numbers of lines of code when compared 
to an existing implementation~\cite{bono14} using plain Java 8. The last
application is a larger case study of refactoring of a simple one-pass compiler, showing that our
approach can scale to real code base. Noteworthy, all applications are implemented 
without defining a single class!

>>>>

To evaluate the usefulness of object interfaces, we illustrate
\numOfCaseStudies \bruno{needs updates}\yanlin{updated} 
applications. The first application is a simple 
solution to the Expression Problem~\cite{wadler98expression}, supporting independent 
extensibility~\cite{zenger05independentlyextensible}, and without boilerplate code. The second
application shows how embedded DSLs using fluent interfaces~\cite{fowler2005fluentinterface} 
can be easily defined using object interfaces. The third
application is a case study for a simple Maze game implemented with 
multiple inheritance. For this application we show that there is a
significant reduction in the numbers of lines of code when compared 
to an existing implementation~\cite{bono14} using plain Java 8. The last
application is a relatively larger case study of refactoring of a simple interpreter, showing that our
approach can benefit modularity and scale to real code base. Noteworthy, the first three applications are implemented 
without defining a single class! The last one contains several classes that cannot be 
converted to interfaces due to the limitation of our implementation of \mixin.
